Zero-shot adaptation by meta-mapping between tasks

### 2019-09-05 writing/embedded_meta_learning_main.tex
Further tweaks

\paragraph{Meta-mapping:} However, the system is not limited to basic meta-learning. The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to recurse on its own representations. From the perspective of our architecture, learning a meta-mapping between tasks is exactly analogous to learning a basic task. Anything that is embedded in $Z$ can be transformed using the same system. Because tasks are embedded in $Z$ for basic meta-learning, this allows for meta-mappings using exactly the same $\mathcal{M}$ and $\mathcal{H}$ that we use for basic tasks. Just as we would take a set of paired embeddings of data points for a basic task, and use them to compute a function embedding for that task, we can take a set of paired function embeddings, and use them to create an embedding for the meta-mapping. We can then use this meta-mapping embedding to transform another task. We can thus behave zero-shot on a novel task based on its relationship to a prior task. \par

@@

This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for game 1. To train a meta-mapping, we minimize the $\ell_2$ loss in the latent space betwen this guessed embedding and the embedding of the target task. Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{new}$ strategy. This is how we evaluate meta-mapping performance -- evaluating the loss of transformed task embeddings on the respective target tasks. \par

>>>>

\paragraph{Meta-mapping:} However, the system is not limited to basic meta-learning. The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to transform its task representations like data (see fig. \ref{architecture_inference_fig}). From the perspective of our architecture, learning a meta-mapping between tasks is exactly analogous to learning a basic task. Anything that is embedded in $Z$ can be transformed using the same system. Because tasks are embedded in $Z$ for basic meta-learning, this allows for meta-mappings using exactly the same $\mathcal{M}$ and $\mathcal{H}$ that we use for basic tasks. Just as we would take a set of paired embeddings of data points for a basic task, and use them to compute a function embedding for that task, we can take a set of paired function embeddings, and use them to create an embedding for the meta-mapping. We can then use this meta-mapping embedding to transform another task. We can thus behave zero-shot on a novel task based on its relationship to a prior task. \par

@@

This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for game 1. To train a meta-mapping, we minimize the $\ell_2$ loss in the latent space betwen this guessed embedding and the embedding of the target task. Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{new}$ strategy, by stepping back down a level of abstraction and actually having it play the game via this embedding. This is how we evaluate meta-mapping performance -- evaluating the loss of transformed task embeddings on the respective target tasks. \par
